Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-04-20 cthpc-2017/paper.tex
Use consistent naming

\begin{abstract}
A holistic design and cost-efficient platform to construct self-driving systems is presented, with an emphasis on Linux-based software architectures for computer vision, control system, and inter-vehicle communication. Starting with an executable specification of autonomous car application, subsequent transformations are performed across different levels of abstraction until the final implementation is achieved. The software partitioning is facilitated through the integration of ROS and OpenCV in the same design environment, as well as closed-loop control algorithms and Linux in the run-time system. We built a rapid prototyping based on fundamentally open source technologies, bill of material (BOM) under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently. Using lane departure and the corresponding performance speedup, we show that our platform reduces the design time, while improving the verification efforts, with the aid of tweaked real-time executives.
\end{abstract}

\section{Introduction}
\section{Related Work}

@@

Moreover, ROS is a open-source collaborative platform. Developers around the world share their research across many field,like navigation, manipulation and perception. Based on this, other developers could save much cost for frastructure and concentrate on their own work.

@@

@@

We built the software PWM kernel module with Xenomai real-time API, we named it KsoftPWM, for this project. With the real-time application, it ensures the precision of KsoftPWM signal generation. Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.

>>>>

\begin{abstract}
A holistic design and cost-efficient platform to construct self-driving systems is presented, with an emphasis on Linux-based software architectures for computer vision, control system, and inter-vehicle communication. Starting with an executable specification of autonomous car application, subsequent transformations are performed across different levels of abstraction until the final implementation is achieved. The software partitioning is facilitated through the integration of ROS and OpenCV in the same design environment, as well as closed-loop control algorithms and Linux in the run-time system. We built a rapid prototyping based on fundamentally open source technologies and hardware under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently. Using lane departure and the corresponding performance speedup, we show that our platform reduces the design time, while improving the verification efforts, with the aid of tweaked real-time executives.
\end{abstract}

\section{Introduction}
As an example of Autonomous vehicles, the Google Car has already succeeded in covering thousands of miles of real-road driving \cite{autonomous}.

\section{Related Work}

@@

Moreover, ROS is an open-source collaborative platform. Developers around the world share their research across many field,like navigation, manipulation and perception. Based on this, other developers could save much cost for frastructure and concentrate on their own work.

@@

\subsection{Software-based PWM}

@@

We built the software PWM kernel module with Xenomai real-time API, named after KsoftPWM. With the real-time application, it ensures the precision of KsoftPWM signal generation. Furthermore, the KsoftPWM was built in kernel space to eliminate the system call overhead from user space.
